\section*{Acknowledgments}
This work on randomized smoothing would not have been possible without the guidance, support, and expertise of several individuals to whom I am deeply grateful.

First and foremost, I would like to express my sincere gratitude to my internship mentor, Blaise Delattre, for his thought-provoking questions and constructive feedback, which have pushed me to think more critically about the implications and applications of our work, and for his meticulous attention to detail has undoubtedly improved the quality of this work and helped me formulate more rigorous proofs for our proposed methods.
His patient guidance, insightful discussions, and unwavering support have been instrumental in shaping this research.

I am also indebted to Dr. Paul Caillon and Pr. Alexandre Allauzen, for their profound knowledge of adversarial robustness and machine learning and for their insightful remarks and recommendations during all the stages of this project.
Their broad perspective on the field of machine learning security and general advice on research methodology have been invaluable in shaping the direction of this work and elevating the quality and relevance of our contributions.

Special Thanks to Erwan Fagnou for his help on the implementation of the code of this paper.

I would like to thank the PRAIRIE institute for this invaluable internship opportunity.

This experience has been invaluable for my academic and professional growth, and I am truly thankful for the opportunity to work with such exceptional mentors and colleagues in the field of randomized smoothing and adversarial robustness.
